Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-06-23 WRITEUP/ms.tex
accted for AP comment

\begin{figure*}[htbp]
 \centering
  \includegraphics[width=0.49\textwidth]{\figpath/{dual_16_ncut_0.53}.pdf}
  \includegraphics[width=0.49\textwidth]{\figpath/{dual_28_ncut_0.53}.pdf}

  \includegraphics[width=0.49\textwidth]{\figpath/{dual_16_ncut_6.81}.pdf}
  \includegraphics[width=0.49\textwidth]{\figpath/{dual_28_ncut_6.81}.pdf}

  \includegraphics[width=0.49\textwidth]{\figpath/{dual_16_ncut_18.96}.pdf}
  \includegraphics[width=0.49\textwidth]{\figpath/{dual_28_ncut_18.96}.pdf}
\caption{
Examples of MCCs (white contours) identified by the clump finder in
\flower during its accreting phase (\Fig{SFH}a), where \flower is dispersion-dominated (left two columns), and 
its quiescent phase, which is rotation-dominated (right two columns).
Leftmost and second left panels show the accreting phase of \flower from different viewing angles. Similarly, for the right two columns
in the quiescent phase.
Colorbar on the right shows the mean H$_2$ number density, weighted by gas mass. 
Different rows show the results obtained by applying different H$_2$ number density cuts $(n_{\rm cut})$ as shown by the label. 
\AP{label with the phase should be included in the first row}
\label{fig:MCC}
}
\end{figure*}

>>>>

\begin{figure*}[htbp]
 \centering
  \includegraphics[width=\textwidth, trim=25 25 35 30, clip]{\figpath/SS_bigfonts/{combined}.pdf}
\caption{
Examples of MCCs (white contours) identified by the clump finder in
\flower during its accreting phase (\Fig{SFH}a; left two columns), where \flower display a highly disturbed gas morphology, and 
its quiescent phase (right two columns), where \flower shows a rotating disk configuration.
Panels in the second and fourth columns show the molecular gas distribution projected along different viewing angles. 
Colorbar on the right shows the mean H$_2$ number density, weighted by gas mass. 
Different rows show the results obtained by applying different H$_2$ number density cuts $(n_{\rm cut})$ as annotated by the label in the bottom left corners. 
\label{fig:MCC}
}
\end{figure*}
